---
title: "Text_similarity example"
output: pdf_document
---

This script includes a simple example of the computation procedure used in my thesis 'Text analysis using colexification networks'. All the results presented in the thesis have been computed using the following steps.

(1) General setup and libraries. Replace the mainpath directory with your directory of the downloaded repository.
```{r, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
mainpath = "C:/Users/Armin/Desktop/Output/"
```

(2) Load helper scripts used for preprocessing the text data files, setting up the similarity matrix used for computing the text similarity and for the text similarity algorithm.
```{r echo=TRUE}
#Preprocessing script
source(sprintf("%sScripts/Computations/prepro_text.R", mainpath))
#Similarity matrix script
source(sprintf("%sScripts/Computations/setup_sim_matrix.R", mainpath))
#Text similarity script
source(sprintf("%sScripts/Computations/text_similarity.R", mainpath))
```

(3) Load text files of the two texts for which the similarity is computed. The texts are in the folder Scripts/Example/. Two random texts from the Project Gutenberg corpus have been chosen to feature in this example.
```{r echo=TRUE}
#Text1
text1 = "PG31178_tokens"
text1_raw = read.csv(paste0(mainpath,"Scripts/Example/",text1,".txt")
                     , sep = "", header = FALSE)
text1 = paste(text1_raw$V1)
text1 = iconv(enc2utf8(text1),sub="byte")
text1 = list(text1[nchar(text1)>0])
#Text2
text2 = "PG40983_tokens"
text2_raw = read.csv(paste0(mainpath,"Scripts/Example/",text2,".txt")
                     , sep = "", header = FALSE)
text2 = paste(text2_raw$V1)
text2 = iconv(enc2utf8(text2),sub="byte")
text2 = list(text2[nchar(text1)>0])
```

(4) Set up the similarity matrix. It loads the raw similarity matrix corresponding to the selected dampening parameter beta and and performs the modification regarding the lower threshold. 
```{r echo=TRUE}
net="combined_clics3based"
beta = 0.8
lower_th = 0.5
sim = setup_sim_matrix(mainpath, net, beta, lower_th)
```

(5) Preprocess texts. This part applies the preprocessing helper script. During this step, punctuations and numeric symbols are removed from the texts.
```{r echo=TRUE}
text1 = prepro_text(text1)
text2 = prepro_text(text2)
```

(6) Compute text similarity. First, 2000 words are sampled from each text in order to represent it without using its full extent. Next, the text similarity algorithm is applied.
```{r echo=TRUE}
#Sample 2000 words from each text
set.seed(1)
text1 = sample(text1, 2000)
set.seed(2)
text2 = sample(text2, 2000)
#Apply similarity algorithm
similarity = suppressMessages(text_sim(mainpath, text1, text2, sim))
print(similarity)
```
